---
title: "03. Predict the intra-respondent reliability (IRR)"
output: rmarkdown::html_vignette
description: >
  How to predict intra-respondent reliability without a repeated task
vignette: >
  %\VignetteIndexEntry{03. Predict the intra-respondent reliability (IRR)}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

When there is a repeated task, it is easy to estimate intra-respondent reliability (IRR). When there is not, however, we use an extrapolation method to estimate it instead.

### 3.1 Load the projoint package

```{r}
library(projoint)
```

### 3.2 Read and wrangle data without the repeated tasks

As before, we start by reshaping our data and setting `.repeated` to `FALSE`:

```{r}
outcomes <- paste0("choice", seq(from = 1, to = 8, by = 1))
out3 <- reshape_projoint(.dataframe = exampleData3, 
                         .idvar = "ResponseId", 
                         .outcomes = outcomes,
                         .outcomes_ids = c("A", "B"),
                         .alphabet = "K", 
                         .repeated = FALSE,
                         .flipped = NULL)
```

### 3.3 Predict IRR based on the extrapolation method

Then, we pass this data set to the `predict_tau` function, which both calculates IRR and produces a figure showing the extrapolation method visually.

```{r}
predicted_irr <- predict_tau(out3)
predicted_irr@irr
predicted_irr@figure
```
