---
title: "05. Visualize MMs or AMCEs"
output: rmarkdown::html_vignette
description: >
  How to visualze the marginal means (MMs) or average marginal component effects (AMCEs)
vignette: >
  %\VignetteIndexEntry{05. Visualize MMs or AMCEs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The `projoint` package features a set of tools for producing publication-ready figures from conjoint analyses.


### 5.1 Load the projoint package

```{r}
library(projoint)
```

### 5.2 Estimate MMs and AMCEs.

```{r}
mm   <- projoint(out1_arranged) 
amce <- projoint(out1_arranged, .estimand = "amce")
```

### 5.3 Visualize MMs and AMCEs

By default, most researchers should prefer to view the corrected estimates of either MMs or AMCEs. Researchers can, however, choose to instead visualize the uncorrected estimates, or to view both together.

```{r, fig.height=8, fig.width=8}
plot_projoint(mm)
plot_projoint(mm, .estimates = "uncorrected")
plot_projoint(mm, .estimates = "both")
```

```{r, fig.height=8, fig.width=8}
plot_projoint(amce, .estimand = "amce")
plot_projoint(amce, .estimand = "amce", .estimates = "uncorrected")
plot_projoint(amce, .estimand = "amce", .estimates = "both")
```
