---
title: "5. Visualize MMs or AMCEs"
output: rmarkdown::html_vignette
description: >
  How to visualze the marginal means (MMs) or average marginal component effects (AMCEs)
vignette: >
  %\VignetteIndexEntry{5. Visualize MMs or AMCEs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The `projoint` package features a set of tools for producing publication-ready figures from conjoint analyses.

### 5.1 Load the projoint package and the other necessary package

```{r}
library(projoint)
library(ggplot2)
```

### 5.2 Profile-level analysis

#### Estimate MMs and AMCEs.

```{r}
mm   <- projoint(out1_arranged) 
amce <- projoint(out1_arranged, .estimand = "amce")
```

#### Visualize MMs and AMCEs

By default, most researchers should prefer to view the corrected estimates of either MMs or AMCEs. Researchers can, however, choose to instead visualize the uncorrected estimates, or to view both together.

```{r, fig.height=8, fig.width=8}
plot(mm)
plot(mm, .estimates = "uncorrected")
plot(mm, .estimates = "both")
```

```{r, fig.height=8, fig.width=8}
plot(amce)
plot(amce, .estimates = "uncorrected")
plot(amce, .estimates = "both")
```

### 5.3 Choice-level analysis

To undertake choice-level analysis, you first need to specify your quantity of interest using `set_qoi()`.
```{r}
qoi_mm <- set_qoi(.structure = "choice_level", 
                  .att_choose = "att1", 
                  .lev_choose = "level1", 
                  .att_notchoose = "att1", 
                  .lev_notchoose = "level3")
```
You can then estimate the choice-level marginal means:
```{r, fig.height=4, fig.width=8}
choice_mm <- projoint(.data = out1_arranged, 
                      .structure = "choice_level", 
                      .qoi = qoi_mm, 
                      .ignore_position = TRUE)

print(choice_mm)
summary(choice_mm)
plot(choice_mm)
```

The default plot for the choice-level marginal means is a basic ggplot object. You can polish by adding some layers :
```{r, fig.height=4, fig.width=8}
plot(choice_mm,
     .labels = c("15% of pre-tax income", 
                 "30% of pre-tax income")) +
  labs(y = "Marginal mean",
       x = "Housing Cost") +
  coord_cartesian(ylim = c(0, 1)) +
  geom_hline(yintercept = 0.5, 
             linetype = "dashed", 
             color = "darkgray")

```

<span style="color:red">Note: The current version of the `projoint` package does not have a function to plot choice-level average marginal compoennt effects. Stay tuned!</span> 
