---
title: "7. Explore further"
output: rmarkdown::html_vignette
description: >
  How to estimate more under-investigated quantities of interest
vignette: >
  %\VignetteIndexEntry{7. Explore further}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The choice-level analysis will allow researchers to examine many more questions under-investigated in the literature. This article explains some possible avenues for fruitful research. 

### 7.1 Load the projoint package and the other necessary package

```{r}
library(projoint)
library(ggplot2)
```

As in the previous articles, we use the already wrangled and cleaned data named "out1_reshaped." To see what the attribute IDs and level IDs means, you can type: 
```{r}
out1_arranged@labels
```


### 7.1 Examine trade-offs

You may be interested in how people make a choice when they face trade-off options. For example, on the one hand, they may want to live in an inexpensive house. On the other hand, they may prefer to avoid living in an area with a high crime rate. Which of these two options would they prefer? You can compare these two options directly. For the customization of the figure, see [Visualize MMs or AMCEs, Choice-level analysis](https://yhoriuchi.github.io/projoint/articles/05-visualize.html#choice-level-analysis)

```{r, fig.height=4, fig.width=8}
qoi_1 <- set_qoi(
  .structure = "choice_level",
  .att_choose = "att1", 
  .lev_choose = "level1",
  .att_notchoose = "att6", 
  .lev_notchoose = "level2"
) 

mm1 <- projoint(.data = out1_arranged,
                .qoi = qoi_1,
                .structure = "choice_level", 
                .ignore_position = TRUE)

plot(mm1,
     .labels = c("Housing Cost\n(15% of pre-tax income)", 
                 "Violent Crime Rate\n(20% > National Average)")) +
  labs(y = "Marginal mean",
       x = NULL) +
  coord_cartesian(ylim = c(0, 1)) +
  geom_hline(yintercept = 0.5, 
             linetype = "dashed", 
             color = "darkgray")
  
```

### 6.1 Set multiple levels for the attribute of interest

You may be interested in measuring the marginal means of choosing more than one level. For example, you may want to estimate the marginal mean of choosing "City, more residential area" OR "City, downtown area" as opposed to "Suburban, only houses" OR "Suburban, downtown area". Then, you can run the following code: 

```{r, fig.height=4, fig.width=8}
qoi_2 <- set_qoi(
  .structure = "choice_level",
  .att_choose = "att7", 
  .lev_choose = c("level2", "level3"),
  .att_notchoose = "att7", 
  .lev_notchoose = c("level5", "level6")
)

mm2 <- projoint(.data = out1_arranged,
                .qoi = qoi_2,
                .structure = "choice_level", 
                .ignore_position = TRUE)

plot(mm2, 
     .labels = c("City", "Suburban")) +
  labs(y = "Marginal mean",
       x = "Type of place") +
  coord_cartesian(ylim = c(0, 1)) +
  geom_hline(yintercept = 0.5, 
             linetype = "dashed", 
             color = "darkgray")
```



