---
title: "Analyze and Visualize Important QOIs"
output: rmarkdown::html_vignette
description: >
  How to estimate and correct marginal means (MMs) or average marginal component effects (AMCEs), including predicting IRR if necessary. Visualize these and other QOIs of interest.
vignette: >
  %\VignetteIndexEntry{Analyze and Visualize Important QOIs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
library(projoint)
library(dplyr)
library(ggplot2)
library(patchwork)
```

## 🎯 Estimate Corrected MMs or AMCEs

In conjoint analysis, default MMs and AMCEs can be **biased** due to measurement error from intra-respondent variability.

**projoint** corrects for this bias automatically.

The following instructions apply to choice-level data. What if you have profile-level data?<sup><a href="faq.html#what-if-i-have-profile-level-data" target="_blank" style="text-decoration: none;">&#9432;</a></sup> Our <a href="faq.html" target="_blank">FAQ Page</a> has instructions to estimate and visualize profile-level QOIs.

---

## 📦 Prepare Example Data

> **Outcome naming & order (important)**
> 
> - List `.outcomes` in the **order questions were asked**.  
> - If you have a repeated task, its outcome must be the **last element**.  
> - For base tasks (all but last), the function reads the **digits** in each name as the task id (e.g., `"choice4"`, `"Q4"`, `"task04"` → task 4).  
> - The **repeated base task** is inferred from the **first base outcome’s digits**. The repeated outcome itself **need not** contain digits—only its position (last) matters.  
> - Outcome strings should end with your choice labels; by default we parse the **last character** and expect `"A"`/`"B"`. If your survey uses `"1"`/`"2"` (or other endings), set `.choice_labels` accordingly.

**Examples**

```{r}
# Standard order; repeated = task 1
outcomes <- c(paste0("choice", 1:8), "choice1_repeated_flipped")
out1 <- reshape_projoint(exampleData1, outcomes)
```

---

## 🛠️ Why Use IDs (e.g., `att1`, `level1`)?

Before estimating quantities, it’s important to understand how attribute and level IDs work inside projoint.

<details>
We recommend working with **attribute IDs** rather than actual text labels because:

- Safer against special characters, languages, or typos
- Allows **multiple attributes** to have identical labels (e.g., "High" for both "Teaching Quality" and "Research Quality")

Check attribute-level mappings:

```{r}
out1$labels
```

You can also save these labels for easier editing:

```r
save_labels(out1, "labels.csv")
```
</details>
---

## 📈 Estimate Marginal Means (MMs)

<details><summary><b>Choice-Level MMs (Specific Level)</b></summary>

Suppose you want to estimate, within a given profile pair, the probability of choosing a profile that includes "40% of pre-tax income" (`level3`) for Housing Cost (`att1`) rather than one that includes "15% of pre-tax income" (`level1`) for the same attribute, averaging over all combinations of the other attributes and across respondents; then use the following code:

```{r}
qoi <- set_qoi(
  .structure = "choice_level",
  .att_choose = "att1",
  .lev_choose = "level3",
  .att_notchoose = "att1",
  .lev_notchoose = "level1"
)

mm2 <- projoint(out1, qoi)
print(mm2)
summary(mm2)
```

</details>
---

## 📉 Estimate AMCEs

<details><summary><b>Choice-Level AMCEs (Specific Level)</b></summary>

Suppose you want to quantify how the choice probability **changes** between the following profile pairs:

- choosing a profile that includes "40% of pre-tax income" (`level3`) for Housing Cost (`att1`) versus one that includes "15% of pre-tax income" (`level1`) for Housing Cost (`att1`); **and**
- [baseline] choosing a profile that includes "30% of pre-tax income" (`level2`) for Housing Cost (`att1`) versus one that includes "15% of pre-tax income" (`level1`) for Housing Cost (`att1`); 

averaging over all combinations of the other attributes and across respondents. Then write the following code:

```{r}
qoi <- set_qoi(
  .structure = "choice_level",
  .estimand = "amce",
  .att_choose = "att1",
  .lev_choose = "level3",
  .att_notchoose = "att1",
  .lev_notchoose = "level1",
  .att_choose_b = "att1",
  .lev_choose_b = "level2",
  .att_notchoose_b = "att1",
  .lev_notchoose_b = "level1"
)

amce2 <- projoint(out1, qoi)
print(amce2)
summary(amce2)
```

</details>
---

## 🔎 Predict Intra-Respondent Reliability (IRR)

If your design **does not include** a repeated task, you can **predict** IRR using predict_tau(), based on observed respondent behavior.

<details><summary><b>Predict IRR Using `predict_tau()`</b></summary>

```{r}
data(out1_arranged)
predicted_irr <- predict_tau(out1_arranged)

print(predicted_irr)
summary(predicted_irr)
plot(predicted_irr)
```

</details>
---

```{r fig-setup, include=FALSE}
# Global default settings for all figures
knitr::opts_chunk$set(
  fig.width = 6,
  fig.height = 3,
  fig.align = "center",
  dpi = 300  # Optional: high-resolution plots
)

# Helper functions for special figure sizes
narrow_fig <- function() list(fig.width = 5, fig.height = 4)
wide_fig <- function() list(fig.width = 8, fig.height = 5)
tall_fig <- function() list(fig.width = 6, fig.height = 7)

```

```{r, echo=FALSE}
library(projoint)
library(ggplot2)

data(out1_arranged, package = "projoint")
```

## 🎨 Visualize MMs or AMCEs

The **projoint** package provides ready-to-publish plotting tools for conjoint analysis results.

<span style="color:DarkRed"><b>Note:</b></span> The current version of **projoint** supports plotting choice-level MMs only.  
Support for **choice-level AMCEs** will be available in future updates!

---

### ⚖️ Choice-Level Analysis

<details>
<summary><b>Estimate</b></summary>

- Specify your quantity of interest:
```{r}
qoi_mm <- set_qoi(
  .structure = "choice_level", # default
  .att_choose = "att1", 
  .lev_choose = "level1", 
  .att_notchoose = "att1", 
  .lev_notchoose = "level3"
)
```

- Estimate
```{r}
choice_mm <- projoint(
  .data = out1_arranged, 
  .qoi = qoi_mm, 
  .ignore_position = TRUE
)
```
</details>

<details>
<summary><b>Visualize (Levels) </b></summary>

```{r, fig.width = 6, fig.height = 3}
plot(choice_mm)
```
</details>

<details>
<summary><b>Visualize (Differences)</b></summary>

```{r, fig.width = 8, fig.height = 2}
plot(choice_mm, .type = "pointrange")
```
</details>

---

## 🌟 Explore and Compare Further

Choice-level analysis opens the door to many **new research questions** that traditional profile-level analysis often overlooks. Below, we demonstrate how to estimate **deeper quantities** and **compare subgroups** effectively.

Depending on your objectives, you may want to reorganize the data in a `projoint_data` object. The helper function below is internal to the package, but you can call it explicitly in your script.”
```{r}
projoint_data <- function(labels, data) {
  structure(
    list(labels = labels, data = data),
    class = "projoint_data"
  )
}
```

---

## 📦 Setup

We use the already wrangled and cleaned data `out1_arranged`.

```{r}
out1_arranged$labels
```

---

## ⚖️ Explore: Compare Trade-offs Directly

<details><summary><b>Example: Low Housing Costs vs. Low Crime Rates</b></summary>

**Goal.** Compare choices between two *joint* profiles:

- **Low housing cost** but **high violent‑crime rate**, versus
- **High housing cost** but **low violent‑crime rate**.

```{r, message=FALSE, warning=FALSE}
# 1) Data: keep only the two joint profiles of interest
d1 <- out1_arranged$data
d2 <- d1 |> 
  mutate(y1 = case_when(
    # Low housing cost, high crime
    att1 == "att1:level1" & att6 == "att6:level2" ~ 1,
    TRUE ~ 0
  ),
  y0 = case_when(
    # High housing cost, low crime
    att1 == "att1:level3" & att6 == "att6:level1" ~ 1,
    TRUE ~ 0
  )) |> 
  filter(y1 == 1 | y0 == 1)

# 2) Labels: rename only the two att1 levels to reflect the joint trade-offs
labels1 <- out1_arranged$labels
labels2 <- labels1 |> 
  mutate(level = case_when(level_id == "att1:level1" ~ "Housing Cost (Low)\nCrime Rate(High)", 
                           level_id == "att1:level3" ~ "Housing Cost (High)\nCrime Rate(Low)", 
                           TRUE ~ level_id))
```


**(Optional) Sanity checks**
```{r}
d1 |> count(att1, att6)
d2 |> count(att1, att6) # only the two joint profiles remain
labels1 |> filter(attribute_id == "att1")
labels2 |> filter(attribute_id == "att1" & level_id %in% c("att1:level1", "att1:level3"))
```

**Recreate a `projoint_data` object, set the QOI, and plot.**
```{r, fig.width = 6, fig.height = 3}
# 3) Build a new projoint_data object
pj_data_wrangled <- projoint_data("labels" = labels2, 
                                  "data" = d2)

# 4) Quantity of interest: Low vs High housing cost under the specified crime conditions (choice-level MM)
qoi <- set_qoi(
  .att_choose = "att1", 
  .lev_choose = "level1", # Low housing cost (with high crime in this subset)
  .att_notchoose = "att1", 
  .lev_notchoose = "level3" # High housing cost (with low crime in this subset)
)

# 5) Estimate and plot (horizontal layout)
out <- projoint(pj_data_wrangled, qoi)
plot(out)
```

</details>

---

## 🧩 Explore: Compare Multiple Levels Simultaneously

<details><summary><b>Example: Urban vs. Suburban Preferences</b></summary>

**Goal.** Collapse `att7` into two buckets—City (levels 1–2) vs. Suburban (levels 5–6)—then re‑estimate and plot.

```{r, message=FALSE, warning=FALSE}
# 1) Data: collapse levels for att7
d1 <- out1_arranged$data
d2 <- d1 |>
  mutate(
    att7 = case_when(
      att7 %in% c("att7:level1", "att7:level2") ~ "att7:level7",  # City
      att7 %in% c("att7:level5", "att7:level6") ~ "att7:level8",  # Suburban
      TRUE ~ att7
    )
  )

# 2) Labels: create matching level IDs and readable names
labels1 <- out1_arranged$labels
labels2 <- labels1 |>
  mutate(
    level_id = case_when(
      level_id %in% c("att7:level1", "att7:level2") ~ "att7:level7",
      level_id %in% c("att7:level5", "att7:level6") ~ "att7:level8",
      TRUE ~ level_id
    ),
    level = case_when(
      level_id == "att7:level7" ~ "City",
      level_id == "att7:level8" ~ "Suburban",
      TRUE ~ level
    )
  ) |>
  distinct()
```


**(Optional) Sanity checks**
```{r}
d1 |> count(att7)
d2 |> count(att7)
labels1 |> filter(attribute_id == "att7")
labels2 |> filter(attribute_id == "att7")
```

**Recreate a `projoint_data` object, set the QOI, and plot.**
```{r, fig.width = 6, fig.height = 3}
# 3) Build a new projoint_data object
pj_data_wrangled <- projoint_data("labels" = labels2, 
                                  "data" = d2)

# 4) Quantity of interest: City vs. Suburban (choice-level MM)
qoi <- set_qoi(
  .structure     = "choice_level",
  .att_choose    = "att7",
  .lev_choose    = "level7",  # City
  .att_notchoose = "att7",
  .lev_notchoose = "level8"   # Suburban
)

# 5) Estimate and plot (horizontal layout)
out <- projoint(pj_data_wrangled, qoi)
plot(out)
```

</details>

---

## 📊 Compare: Subgroup Differences

<details><summary><b>Choice-Level Subgroup Comparison: Party Differences</b></summary>

```{r, fig.height=4, fig.width=8}
df_D <- exampleData1 |> filter(party_1 == "Democrat") |> reshape_projoint(outcomes)
df_R <- exampleData1 |> filter(party_1 == "Republican") |> reshape_projoint(outcomes)
df_0 <- exampleData1 |> filter(party_1 %in% c("Something else", "Independent")) |> reshape_projoint(outcomes)

qoi <- set_qoi(
  .structure = "choice_level",
  .estimand = "mm",
  .att_choose = "att2",
  .lev_choose = "level3",
  .att_notchoose = "att2",
  .lev_notchoose = "level1"
)

out_D <- projoint(df_D, qoi)
out_R <- projoint(df_R, qoi)
out_0 <- projoint(df_0, qoi)

out_merged <- bind_rows(
  out_D$estimates |> mutate(party = "Democrat"),
  out_R$estimates |> mutate(party = "Republican"),
  out_0$estimates |> mutate(party = "Independent")
) |> filter(estimand == "mm_corrected")

# Plot

ggplot(out_merged, aes(y = party, x = estimate)) +
  geom_vline(xintercept = 0.5, linetype = "dashed", color = "gray") +
  geom_pointrange(aes(xmin = conf.low, xmax = conf.high)) +
  geom_text(aes(label = format(round(estimate, 2), nsmall = 2)), vjust = -1) +
  labs(y = NULL, x = "Choice-level Marginal Mean",
       title = "Preference for Democratic-majority areas") +
  theme_classic()
```

</details>

---

🏠 **Home:** [Home](../index.html)

