---
title: "Analyze and Visualize Important QOIs"
output: rmarkdown::html_vignette
description: >
  How to estimate and correct marginal means (MMs) or average marginal component effects (AMCEs), including predicting IRR if necessary. Visualize these and other QOIs of interest.
vignette: >
  %\VignetteIndexEntry{Analyze and Visualize Important QOIs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
library(projoint)
library(dplyr)
library(ggplot2)
library(patchwork)
```

## 🎯 Estimate Corrected MMs or AMCEs

In conjoint analysis, default MMs and AMCEs can be **biased** due to measurement error from intra-respondent variability.

**projoint** corrects for this bias automatically.

The following instructions apply to choice-level data. What if you have profile-level data?<sup><a href="faq.html#what-if-i-have-profile-level-data" target="_blank" style="text-decoration: none;">&#9432;</a></sup> Our <a href="faq.html" target="_blank">FAQ Page</a> has instructions to estimate and visualize profile-level QOIs.

---

## 📦 Prepare Example Data

```{r}
outcomes <- paste0("choice", 1:8)
outcomes <- c(outcomes, "choice1_repeated_flipped")
out1 <- reshape_projoint(exampleData1, outcomes)
```

---

## 🛠️ Why Use IDs (e.g., `att1`, `level1`)?

Before estimating quantities, it’s important to understand how attribute and level IDs work inside projoint.

<details>
We recommend working with **attribute IDs** rather than actual text labels because:

- Safer against special characters, languages, or typos
- Allows **multiple attributes** to have identical labels (e.g., "High" for both "Teaching Quality" and "Research Quality")

Check attribute-level mappings:

```{r}
out1$labels
```

You can also save these labels for easier editing:

```r
save_labels(out1, "labels.csv")
```
</details>
---

## 📈 Estimate Marginal Means (MMs)

<details><summary><b>Choice-Level MMs (Specific Level)</b></summary>

```{r}
qoi_2 <- set_qoi(
  .structure = "choice_level",
  .att_choose = "att1",
  .lev_choose = "level3",
  .att_notchoose = "att1",
  .lev_notchoose = "level1"
)

mm2 <- projoint(out1, .qoi = qoi_2, .ignore_position = FALSE)
print(mm2)
summary(mm2)
```

</details>
---

## 📉 Estimate AMCEs

<details><summary><b>Choice-Level AMCEs (Specific Level)</b></summary>

```{r}
qoi_4 <- set_qoi(
  .structure = "choice_level",
  .estimand = "amce",
  .att_choose = "att1",
  .lev_choose = "level3",
  .att_notchoose = "att1",
  .lev_notchoose = "level1",
  .att_choose_b = "att1",
  .lev_choose_b = "level2",
  .att_notchoose_b = "att1",
  .lev_notchoose_b = "level1"
)

amce2 <- projoint(out1, .qoi = qoi_4, .ignore_position = TRUE)
print(amce2)
summary(amce2)
```

</details>
---

## 🔎 Predict Intra-Respondent Reliability (IRR)

If your design **does not include** a repeated task, you can **predict** IRR using predict_tau(), based on observed respondent behavior.

<details><summary><b>Predict IRR Using `predict_tau()`</b></summary>

```{r}
data(out1_arranged)
predicted_irr <- predict_tau(out1_arranged)

print(predicted_irr)
summary(predicted_irr)
plot(predicted_irr)
```

</details>
---

```{r fig-setup, include=FALSE}
# Global default settings for all figures
knitr::opts_chunk$set(
  fig.width = 6,
  fig.height = 3,
  fig.align = "center",
  dpi = 300  # Optional: high-resolution plots
)

# Helper functions for special figure sizes
narrow_fig <- function() list(fig.width = 5, fig.height = 4)
wide_fig <- function() list(fig.width = 8, fig.height = 5)
tall_fig <- function() list(fig.width = 6, fig.height = 7)

```

```{r, echo=FALSE}
library(projoint)
library(ggplot2)

data(out1_arranged, package = "projoint")
```

## 🎨 Visualize MMs or AMCEs

The **projoint** package provides ready-to-publish plotting tools for conjoint analysis results.

<span style="color:DarkRed"><b>Note:</b></span> The current version of **projoint** supports plotting choice-level MMs only.  
Support for **choice-level AMCEs** will be available in future updates!

---

### ⚖️ Choice-Level Analysis

<details>
<summary><b>Estimate</b></summary>

- Specify your quantity of interest:
```{r}
qoi_mm <- set_qoi(
  .structure = "choice_level", # default
  .att_choose = "att1", 
  .lev_choose = "level1", 
  .att_notchoose = "att1", 
  .lev_notchoose = "level3"
)
```

- Estimate
```{r}
choice_mm <- projoint(
  .data = out1_arranged, 
  .qoi = qoi_mm, 
  .ignore_position = TRUE
)
```
</details>

<details>
<summary><b>Visualize (Levels) </b></summary>

```{r, fig.width = 6, fig.height = 3}
plot(choice_mm)
```
</details>

<details>
<summary><b>Visualize (Differences)</b></summary>

```{r, , fig.width = 8, fig.height = 2}
plot(choice_mm, .type = "pointrange")
```
</details>

---

## 🌟 Explore and Compare Further

Choice-level analysis opens the door to many **new research questions** that traditional profile-level analysis often overlooks.
This article demonstrates how to estimate **deeper quantities** and **compare subgroups** effectively.

---

## 📦 Setup

We use the already wrangled and cleaned data `out1_arranged`.

```{r}
out1_arranged$labels
```

---

## ⚖️ Explore: Compare Trade-offs Directly

<details><summary><b>Example: Low Housing Costs vs. Low Crime Rates</b></summary>

```{r, fig.height=4, fig.width=8}
qoi_1 <- set_qoi(
  .structure = "choice_level",
  .att_choose = "att1",
  .lev_choose = "level1",
  .att_notchoose = "att6",
  .lev_notchoose = "level2"
)

mm1 <- projoint(.data = out1_arranged,
                .qoi = qoi_1,
                .structure = "choice_level",
                .ignore_position = TRUE)

plot(mm1,
     .labels = c("Housing Cost\n(15% of pre-tax income)",
                 "Violent Crime Rate\n(20% > National Average)")) +
  labs(y = "Marginal Mean", x = NULL) +
  coord_cartesian(ylim = c(0, 1)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "darkgray")
```

</details>

---

## 🧩 Explore: Compare Multiple Levels Simultaneously

<details><summary><b>Example: Urban vs. Suburban Preferences</b></summary>

```{r, fig.height=4, fig.width=8}
qoi_2 <- set_qoi(
  .structure = "choice_level",
  .att_choose = "att7",
  .lev_choose = c("level2", "level3"),
  .att_notchoose = "att7",
  .lev_notchoose = c("level5", "level6")
)

mm2 <- projoint(.data = out1_arranged,
                .qoi = qoi_2,
                .structure = "choice_level",
                .ignore_position = TRUE)

plot(mm2,
     .labels = c("City", "Suburban")) +
  labs(y = "Marginal Mean", x = "Type of Place") +
  coord_cartesian(ylim = c(0, 1)) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "darkgray")
```

</details>

---

## 📊 Compare: Subgroup Differences

<details><summary><b>Choice-Level Subgroup Comparison: Party Differences</b></summary>

```{r, fig.height=4, fig.width=8}
df_D <- exampleData1 %>% filter(party_1 == "Democrat") %>% reshape_projoint(outcomes)
df_R <- exampleData1 %>% filter(party_1 == "Republican") %>% reshape_projoint(outcomes)
df_0 <- exampleData1 %>% filter(party_1 %in% c("Something else", "Independent")) %>% reshape_projoint(outcomes)

qoi <- set_qoi(
  .structure = "choice_level",
  .estimand = "mm",
  .att_choose = "att2",
  .lev_choose = "level3",
  .att_notchoose = "att2",
  .lev_notchoose = "level1"
)

out_D <- projoint(df_D, qoi)
out_R <- projoint(df_R, qoi)
out_0 <- projoint(df_0, qoi)

out_merged <- bind_rows(
  out_D$estimates %>% mutate(party = "Democrat"),
  out_R$estimates %>% mutate(party = "Republican"),
  out_0$estimates %>% mutate(party = "Independent")
) %>% filter(estimand == "mm_corrected")

# Plot

ggplot(out_merged, aes(y = party, x = estimate)) +
  geom_vline(xintercept = 0.5, linetype = "dashed", color = "gray") +
  geom_pointrange(aes(xmin = conf.low, xmax = conf.high)) +
  geom_text(aes(label = format(round(estimate, 2), nsmall = 2)), vjust = -1) +
  labs(y = NULL, x = "Choice-level Marginal Mean",
       title = "Preference for Democratic-majority areas") +
  theme_classic()
```

</details>

---
 
🏠 **Home:** [Home](../index.html)

