---
title: "specified-tau"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{specified-tau}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


While our primary recommendation is that researchers conducting a conjoint survey with $n$ tasks include a task $n+1$ that duplicates their first task in order to measure intra-respondent reliability $\tau$, researchers who wish to re-analyze their results from a survey without a repeated task may choose to assume our empirically-estimated $\tau$ instead.

First read the data and inspect it:

```{r setup}
library(projoint)

data("exampleData2")
head(exampleData2)

```

This data frame is the result of a raw data set processed with the \texttt{read_Qualtrics} function. Next we reshape it by specifying the variable indicating respondent IDs and the variables containing outcomes. The \texttt{.alphabet} argument specifies the letter indicating attributes and levels, which defaults to \texttt{F} if using Anton Strezhnev's tool for designing conjoint surveys in Qualtrics. 

```{r reshape}
reshaped_data = reshape_conjoint(exampleData1, .idvar = "ResponseId",
                                 .outcomes = c("Q4.1", "Q5.1", "Q6.1", "Q7.1", "Q8.1", 
                                               "Q9.1"),
                                 .alphabet ="A")

```

Next we use this reshaped data set to estimate marginal means (MMs):

```{r estimate}
results = pj(reshaped_data, .tau = 0.75)


```