---
title: "Wrangle Your Data"
output: rmarkdown::html_vignette
description: >
  How to read and reshape data for conjoint analysis
vignette: >
  %\VignetteIndexEntry{Wrangle Your Data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r fig-setup, include=FALSE}
# Global default settings for all figures
knitr::opts_chunk$set(
  fig.width = 7,
  fig.height = 5,
  fig.align = "center",
  dpi = 300  # Optional: high-resolution plots
)

# Helper functions for special figure sizes
narrow_fig <- function() list(fig.width = 5, fig.height = 4)
wide_fig <- function() list(fig.width = 8, fig.height = 5)
tall_fig <- function() list(fig.width = 6, fig.height = 7)

# Load libraries
library(projoint)
data(exampleData1, package = "projoint")
data(exampleData2, package = "projoint")
data(exampleData3, package = "projoint")
data(exampleData1_labelled_tibble, package = "projoint")
data(out1_arranged, package = "projoint")

```

## 🛠️ Wrangle Your Data

Preparing your data correctly is one of the most important steps in conjoint analysis. Fortunately, the `reshape_projoint()` function in **projoint** makes this easy.

---

## 🚀 Quick Workflow

<!-- <details> -->
<summary><b>1. Reshape Your Data</b></summary>

### Example (Flipped Repeated Task)

```{r, error=TRUE}
outcomes <- paste0("choice", 1:8)
outcomes1 <- c(outcomes, "choice1_repeated_flipped")

out1 <- reshape_projoint(
  .dataframe = exampleData1,
  .outcomes = outcomes1,
  .choice_labels = c("A", "B"),
  .alphabet = "K",
  .idvar = "ResponseId",
  .repeated = TRUE,
  .flipped = TRUE
)
```

**Key Arguments**:

- `.outcomes`: Outcome columns (include repeated task last)
- `.choice_labels`: Profile labels (e.g., "A", "B")
- `.idvar`: Respondent ID variable
- `.alphabet`: Variable prefix ("K")
- `.repeated`, `.flipped`: If repeated task exists and is flipped


<!-- </details> -->

<!-- <details> -->
<summary><b>2. Variations: Repeated vs. Non-Repeated</b></summary>

**Not-Flipped Repeated Task**

```{r}
outcomes <- paste0("choice", 1:8)
outcomes2 <- c(outcomes, "choice1_repeated_notflipped")
out2 <- reshape_projoint(
  .dataframe = exampleData2,
  .outcomes = outcomes2,
  .repeated = TRUE,
  .flipped = FALSE
)
```

**No Repeated Task**

```{r}
outcomes <- paste0("choice", 1:8)
out3 <- reshape_projoint(
  .dataframe = exampleData3,
  .outcomes = outcomes,
  .repeated = FALSE
)
```

<!-- </details> -->

<!-- <details> -->
<summary><b>3. The `.fill` Argument: Should You Use It?</b></summary>

Use `.fill = TRUE` to "fill" missing values based on IRR agreement.

```{r}
fill_FALSE <- reshape_projoint(
  .dataframe = exampleData1,
  .outcomes = outcomes1,
  .fill = FALSE
)

fill_TRUE <- reshape_projoint(
  .dataframe = exampleData1,
  .outcomes = outcomes1,
  .fill = TRUE
)
```

Compare:

```{r}
selected_vars <- c("id", "task", "profile", "selected", "selected_repeated", "agree")
fill_FALSE$data[selected_vars]
fill_TRUE$data[selected_vars]
```

**Tip:**  
- Use `.fill = TRUE` for small-sample or subgroup analysis (helps increase power).  
- Use `.fill = FALSE` (default) when in doubt for safer estimates.

<!-- </details> -->


<!-- <details> -->
<summary><b>4. What If Your Data Is Already Clean?</b></summary>

If you already have a clean dataset, use `make_projoint_data()`:

```{r}
out4 <- make_projoint_data(
  .dataframe = exampleData1_labelled_tibble,
  .attribute_vars = c(
    "School Quality", "Violent Crime Rate (Vs National Rate)",
    "Racial Composition", "Housing Cost",
    "Presidential Vote (2020)", "Total Daily Driving Time for Commuting and Errands",
    "Type of Place"
  ),
  .id_var = "id",
  .task_var = "task",
  .profile_var = "profile",
  .selected_var = "selected",
  .selected_repeated_var = "selected_repeated",
  .fill = TRUE
)
```

Preview:

```{r}
out4
```

<!-- </details> -->


<!-- <details> -->
<summary><b>5. Arranging Attribute and Level Labels</b></summary>

To reorder or relabel attributes:

1. Save labels:

```{r, eval=FALSE}
save_labels(out1, "temp/labels_original.csv")
```

2. Edit the CSV (change `order`, label columns; leave `level_id` untouched)

3. Save it as "labels_arranged.csv" or something else.

4. Reload labels:

```{r, eval=FALSE}
data(out1_arranged, package = "projoint")
```

Compare using our example:

```{r}
mm <- projoint(out1, .structure = "profile_level", .estimand = "mm")
plot(mm)
```

```{r}
mm <- projoint(out1_arranged, .structure = "profile_level", .estimand = "mm")
plot(mm)
```

<!-- </details> -->

---

## 🌟 What's Next?

Now that your data is properly structured, you’re ready to estimate Marginal Means (MMs) or AMCEs!

➡️ **Continue to:** [Analyze Your Conjoint Data](analyze.html)  
⬅️ **Back to:** [Read Your Qualtrics Data](read.html)  
🏠 **Home:** [Home](index.html)

---

