---
title: "2. Read and wrangle your data for conjoint analysis"
output: rmarkdown::html_vignette
description: >
  How to read and reshape data for conjoint analysis
vignette: >
  %\VignetteIndexEntry{2. Read and wrangle your data for conjoint analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Most of the work in analyzing a conjoint task is correctly specifying the data and columns. In `projoint`, the `reshape_projoint` function makes it easy!

### 2.1 Load the projoint package

```{r}
library(projoint)
```

### 2.2 Read and wrangle data

#### With the flipped repeated tasks

Let's look at a simple example. We expand all those arguments below for clarity:

```{r}
outcomes <- paste0("choice", seq(from = 1, to = 8, by = 1))
outcomes1 <- c(outcomes, "choice1_repeated_flipped")
out1 <- reshape_projoint(.dataframe = exampleData1, 
                         .outcomes = outcomes1,
                         .outcomes_ids = c("A", "B"),
                         .alphabet = "K", 
                         .idvar = "ResponseId", 
                         .repeated = TRUE,
                         .flipped = TRUE, 
                         .covariates = NULL,
                         .fill = FALSE)
```

Let's walk through the arguments we have specified. `.dataframe` is a data frame, ideally read in from Qualtrics using `read_Qualtrics()` but not necessarily. The `.idvar` argument, a character, indicates that in `exampleData1`, the column `ResponseId` indicates unique survey respondents. The `.outcomes` variable lists all the columns that are outcomes; the last element in this vector is the repeated task (if it was conducted). `.outcomes_ids` indicates the possible options for an outcome; specifically, it is a vector of characters with two elements, which are the last characters of the names of the first and second profiles. For example, it should be c("A", "B") if the profile names are "Candidate A" and "Candidate B". This character vector can be anything, such as c("1", "2"), c("a", "b"), etc. *If you have multiple tasks in your design, you should use the same profile names across all these tasks*. `.alphabet` defaults to "K" if the conjoint survey was conducted using either our tool or Strezhnev's [Conjoint Survey Design Tool](https://github.com/astrezhnev/conjointsdt). The final two arguments, `.repeated` and `.flipped`, again relate to the repeated task. If the `.repeated` is set to `TRUE`, then the last element of the `.outcomes` vector is taken to be a repetition of the first task; `.flipped` indicates whether the profiles are in the reversed order. See Section 2.3 for `.fill`. 

#### With the not-flipped repeated tasks

As a slight variation, in some cases the repeated task is *not* flipped -- that is, in the repeated task, the original Profile 1 is still Profile 1, rather than flipping positions to Profile 2. Here we specify that by changing `.flipped` to `FALSE`. In the following, we drop the default arguments.

```{r}
outcomes2 <- c(outcomes, "choice1_repeated_notflipped")
out2 <- reshape_projoint(.dataframe = exampleData2, 
                         .outcomes = outcomes2,
                         .repeated = TRUE,
                         .flipped = FALSE)
```

#### Without the repeated tasks

Or in cases with no repeated task at all, we set `.repeated` to `FALSE` and  `.flipped` to `NULL`. Don't worry, we can still correct for measurement error using an extrapolation method; see our third vignette for details.

```{r}
out3 <- reshape_projoint(.dataframe = exampleData3, 
                         .outcomes = outcomes,
                         .repeated = FALSE)
```


### 2.3 The `.fill` argument

The `.fill` argument is logical: TRUE if you want to use information about whether a respondent chose the same profile for the repeated task and "fill" (using the 'tidyr' package) missing values for the non-repeated tasks, FALSE (otherwise). 

You can see the difference by comparing the results of `reshape_projoint` when `.fill` is either `TRUE` or `FALSE`. 

```{r}
fill_FALSE <- reshape_projoint(.dataframe = exampleData1, 
                               .outcomes = outcomes1,
                               .fill = FALSE)
fill_TRUE <- reshape_projoint(.dataframe = exampleData1, 
                              .outcomes = outcomes1,
                              .fill = TRUE)
```
Looking only at a subset of the variables, we can see that the first data frame includes the values for the `agree` variable (whether the same profile was chosen or not) only for the repeated task. The second data frame fills the missing values for the other non-repeated tasks.

```{r}
selected_vars <- c("id", "task", "profile", "selected", "selected_repeated", "agree")
fill_FALSE@data[selected_vars]
fill_TRUE@data[selected_vars]
```

If the number of respondents is small, if the number of specific profile pairs of your interest is small, and/or if the number of specific respondent subgroups you want to study is small, it is worth changing this option to TRUE. But please note that `.fill = TRUE` is based on an assumption that IRR is independent of information contained in conjoint tables. Although our empirical tests suggest the validity of this assumption, if you are unsure about it, it is better to use the default value (FALSE).

### 2.4 What if your data is already clean?

If you have already downloaded your data set from Qualtrics, loaded it into R, and cleaned it, then you can use  `make_projoint_data()` to save your data frame or tibble as a `projoint_data` object for use with the `projoint()`. Here is an example. First, load your data frame. 
```{r}
data <- exampleData1_labelled_tibble
```


It should look like the tibble below. Each row should correspond to one profile from one task for one respondent. The data frame should have columns indicating (1) the respondent ID, (2) task number, (3) profile number, (4) attributes, and (5) a column recording each response (0, 1) for each task. If your design includes the repeated task, it should also include a column recording the response for the repeated task. In this case, that column is `select_repeated`.


```{r}
options(tibble.width = Inf)
data
```

Next, make a character vector of your attributes. 
```{r}
attributes <- c("School Quality",
                "Violent Crime Rate (Vs National Rate)",
                "Racial Composition",
                "Housing Cost",
                "Presidential Vote (2020)",
                "Total Daily Driving Time for Commuting and Errands",
                "Type of Place")
```

With your data frame and attributes vector, you can use `make_projoint_data()` to produce a `projoint_data` object. We can see above that the column indicating the respondent ID is called `id`, so we pass that to the `.id_var` argument of `make_projoint_data`. `id` is also the default for that argument.

```{r, message=FALSE}
out4 <- make_projoint_data(.dataframe = data,
                           .attribute_vars = attributes, 
                           .id_var = "id", # the default name
                           .task_var = "task", # the default name
                           .profile_var = "profile", # the default name
                           .selected_var = "selected", # the default name
                           .selected_repeated_var = "selected_repeated", # the default is NULL
                           .fill = TRUE)
```

The output from this function should look the same as the output of `fill_FALSE` in the previous section.

```{r}
out4
```


### 2.5 Arrange the order and labels of attributes and levels

By default, reshaped data will have attributes and levels that are ordered alphabetically. If you would like to reorder or relable those attributes or levels, we make that process easy.

You first save the labels using `save_labels()`, which produces a CSV file. In that CSV file saved to your local computer, you should revise the column named `order` to specify the order of attributes and levels you want to display in your figure. You can also revise the labels for attributes and levels in any way you like. But *you should not make any change to the first column named `level_id`*. After saving the updated CSV file, you can use `read_labels()` to read in the modified CSV. We will use this object later in the  `projoint` function.

```{r, eval=FALSE}
save_labels(out1, "temp/labels_original.csv")
out1_arranged <- read_labels(out1, "temp/labels_arranged.csv")
```

```{r, echo=FALSE}
data_file <- system.file("extdata", "labels_arranged.csv", package = "projoint")
if (data_file == "") stop("File not found!")
out1_arranged <- read_labels(out1, data_file)
```

You can find this data set on GitHub: [labels_original.csv](https://github.com/yhoriuchi/projoint/blob/master/data-raw/labels_original.csv) and [labels_arranged.csv](https://github.com/yhoriuchi/projoint/blob/master/data-raw/labels_arranged.csv).

The figure based on the original order and labels is in the alphabetical order:
```{r, fig.height=8, fig.width=8}
mm <- projoint(out1, .estimand = "mm")
plot(mm)
```

The labels and order of all attribute-levels in the second figure is the same as Figure 2 in [Mummolo and Nall (2017)](https://doi.org/10.1086/687569).
```{r, fig.height=8, fig.width=8}
mm <- projoint(out1_arranged, .estimand = "mm")
plot(mm)
```



